---
title: "Axis, Legends and Annotations"
output: html_document
date: "2024-03-16"
---

### Introduction:

When constructing a data visualization, it is often necessary to make annotations to the data displayed. Annotations are nothing but the meta-data for the plot. They provide additional contextual information to the plot such as:

 - Char title
 - Axis labels
 - Text labels to the graph
 - Legends
 - Axis tick mark labels and their placements
 - Colors in plots

### Load the libraries

We will work on `gapminder` data, hence loading `gapminder` and `tidyverse` library.
```{r}

library(tidyverse)
library(gapminder)

```

### Display the data
```{r}
head(gapminder)
```

### Add Annotation to scatter plot

```{r}

```

### Remove the overlap of Annotated text

```{r}

```

### Annotate the outliers

```{r}

```

### Change the legend title

```{r}

```

### Changing the Axis labels

```{r}

```

### Add plot title 

```{r}

```

### Change the axis tick scales

```{r}

```

### Rotate the axis tick labels

```{r}

```

### Add different color palette to the chart

```{r}

```





