---
title: "How to create Bar chart using ggplot2 package"
author: "Siddharth"
date: "`r Sys.Date()`"
output: html_document
---

## Load the data-set

```{r}
head(IMDB_Movies)

```

## Create bar chart

```{r}
ggplot(data=IMDB_Movies)+
  aes(x=Genre)+
  geom_bar(stat="count")

```

## Create bar chart for revenue

```{r}
IMDB_Movies %>%
  group_by(Genre) %>%
  summarise(total_revenue = sum(`Gross Revenue`))%>%
  mutate(total_revenue = round((total_revenue*10^-6),2),
         Genre = factor(Genre))%>%
  ggplot()+
  aes(x=fct_reorder(Genre,total_revenue),y=total_revenue,)+
  geom_bar(stat="identity")+
  geom_text(aes(label = total_revenue), vjust = -0.5, colour = "red")

```

## Create bar chart data labels

```{r}
IMDB_Movies %>%
  group_by(Genre) %>%
  summarise(total_revenue = sum(`Gross Revenue`))%>%
   mutate(total_revenue = round((total_revenue*10^-6),2))%>%
  ggplot()+
  aes(x=Genre,y=total_revenue)+
  geom_bar(stat="identity")+
  geom_text(aes(label = total_revenue), vjust = -0.5, colour = "red")


```

## Display bar chart in descending order

```{r}
IMDB_Movies %>%
  group_by(Genre) %>%
  summarise(total_revenue = sum(`Gross Revenue`))%>%
   mutate(total_revenue = round((total_revenue*10^-6),2),
          Genre=factor(Genre))%>%
  ggplot()+
  aes(x=fct_reorder(Genre,total_revenue),Genre,y=total_revenue)+
  geom_bar(stat="identity")+
  geom_text(aes(label = total_revenue), hjust = -0.2, colour = "red")+
  coord_flip()+
  theme_bw()

```

## Summary:

bar chart is created using statistical transformations. stat="count" transformation is used to count the number of observations in the data set for particular category. stat="identity" transformation is used when raw observations are used in bar chart.

the bar chart should be displayed either in ascending or in descending order of the values. The ordering can be changed by converting categorical variable into factor

the axis of bar chart can be interchanged using coord_flip() method
