---
title: "How to create Box Plot and Violine Plot using ggplot2 package?"
author: "Siddharth"
date: "`r Sys.Date()`"
output: html_document
---

### Load the `housing price` data-set

```{r}
library(tidyverse)
housing_price <- read.csv("homeprices.csv")
head(housing_price)
```

### The Box-Whisker Plot for single variable

```{r}
ggplot(data=housing_price)+
  aes(x=factor(Bedrooms),y=Sale.price)+
  geom_boxplot()
```

### The grouped Box-Whisker Plot 

```{r}
ggplot(data=housing_price)+
  aes(x=interaction(factor(Bedrooms),factor(Year.built)),y=Sale.price)+
  geom_boxplot()
```

### The Violine plot

```{r}
ggplot(data=housing_price)+
  aes(x=factor(Bedrooms),y=Sale.price)+
  geom_violin()
```

### The Violine plot overlaid with Box-Whisker plot

```{r}
ggplot(data=housing_price)+
  aes(x=factor(Bedrooms),y=Sale.price)+
  geom_violin()+
  geom_boxplot(width=0.1,fill="black")+
  stat_summary(fun.y=median,geom="point",fill="white",shape=21,size=2.5)
```

## Summary:

-   The box-whisker plot uses five number summary to visualise the shape of the distribution of continuous variable. The five number summary is: min,max,median and first and third quartile of the data..
-   The outliers in the data are shown as dots outside the length of whiskers.
-   box-whisker plots are plotted using `geom_box` gemoetric object
-   box-whisker plots does not show the summary of the data. if we want to see the data distribution along with the summary statistics of the box-plot, we will use violine plots.
-   Violine plots are plotted using `geom_violin` gemoetric object
-   typically, Violine plots also have narrow box plots overlaid
