---
title: "Understanding grammar of graphics design philosophy of ggplot2 package"
author: "Siddharth"
date: "`r Sys.Date()`"
output: html_document
---

`ggplot2` is most popular package for data visualization. This package is part of tidyverse family of packages.

```{r}

library(tidyverse)
```

`ggplot2` layout is based on Grammar of Graphics Design philosophy. Each graph gets created using set of independent components called layers, that can be composed in many different ways.

The main layers are:

-   The dataset layer

-   The aesthetic layer

-   The geometric object layer

-   If needed, additional layers (such as labels, annotations, scales, axis ticks, legends, themes, facets, etc.) can be added to personalize the plot.

## Load the data

```{r}

view(diamonds)
 
```

## Create the ggplot, data and aesthetic layers

```{r}

ggplot(data=diamonds) +
  aes(x = carat, y = price)
 
```

## Create geometric objects

```{r}

ggplot(data=diamonds) +
  aes(x = carat, y = price) +
  geom_point()
   
```

## Use color aesthetic

```{r}

ggplot(data=diamonds) +
  aes(x = carat, y = price, color=cut) +
  geom_point()

```

## Create layer for axis labels and graph title

```{r}

ggplot(data=diamonds) +
  aes(x = carat, y = price, color=cut) +
  geom_point() +
  labs(x= "diamond_weight" ,y = "diamond_price", title = "diamond weight Vs Price")

```

## Create layer for generating sub-plot

```{r}

ggplot(data=diamonds) +
  aes(x = carat, y = price) +
  geom_point() +
  labs(x= "diamond_weight" ,y = "diamond_price", title = "diamond weight Vs Price") +
  facet_wrap(~cut)

```

## Summary:

-   `ggplot2` layout is based on Grammar of Graphics Design philosophy. Each graph gets created using set of independent components called layers, that can be composed in many different ways.

-   The three layers are mandatory to create any chart in ggplot2 package

    -   dataset layer

    -   aesthetic layer

    -   geometric object layer
