---
title: "histogram and density plot"
output: html_document
date: "`r Sys.Date()`"
---

### What is Histogram?
Histograms are graphs of a distribution of single continuous variable designed to show centering, dispersion (spread), and shape (relative frequency) of the data. Histograms can provide a visual display of large amounts of data that are difficult to understand in a tabular, or spreadsheet form. 

## Load the library and data set

```{r}

library(tidyverse)
library(datasets)

head(rivers)

df_rivers <- data.frame(rivers)%>% view
```

## Create histogram for `rivers` variable

```{r}
ggplot(data=df_rivers)+
  aes(x=rivers)+
  geom_histogram(fill="white",color="black")+
  geom_vline(xintercept = mean(df_rivers$rivers),lwd=1,linetype=2,color="red")

```

## Create frequency polygon

```{r}
ggplot(data=df_rivers)+
  aes(x=rivers)+
  geom_histogram(fill="white",color="black")+
  geom_vline(xintercept = mean(df_rivers$rivers),lwd=1,linetype=2,color="red")+
  geom_freqpoly(color="blue",lwd=1)

```

## Load the data set

```{r}
head(geyser)
```

## Create histogram for `duration` variable


```{r}
ggplot(data=geyser)+
  aes(x=duration)+
  geom_histogram(color="black",fill="white",binwidth = 0.25,boundary=2)+
  geom_vline(xintercept = mean(geyser$duration),lwd=1,color="red",linetype=2)

```

## Create Frequency polygon

```{r}
ggplot(data=geyser)+
  aes(x=duration)+
  geom_histogram(color="black",fill="white",binwidth = 0.25,boundary=2)+
  geom_vline(xintercept = mean(geyser$duration),lwd=1,color="red",linetype=2)+
  geom_freqpoly(color="blue",lwd=1,binwidth=0.25,boundary=2)
```

### Summary:
  - Histograms are graphs of a distribution of single continuous variable designed to show centering, dispersion        (spread),and shape (relative frequency) of the data.
  
  - Histograms are created using `geom_histogram` geometric object. 
  
  -  Histogram divides the x-axis into bins and counting the number of observations in each bin.
  
  - By default,number of bins are 30, but it can be changed using `binwidth` argument 
  
  - `boundry` argument is used to specify the bin position
  
  - `geom_density` geometric object is used to draw smooth curves to show the general shape of the                      distribution
