---
title: "Line chart with ggplot2"
author: "Siddharth"
date: "`r Sys.Date()`"
output: html_document
---

A line chart represents a series of data points connected by a straight line, with the x-axis representing time and the y-axis representing the data value.

## Load the Packages

```{r}


```

## Load the Data-set

```{r}


```

## Wrangle the data

```{r}


```

## Plot the line chart

```{r}


```

## Transform the data

```{r}


```

## Plot line chart with color aesthetics

```{r}


```

## Change line chart appearance with data point

```{r}

```

## Draw area chart

```{r}


```

## Add confidence region to line chart

```{r}


```

# Summary:

-   Line plots are widely used to visualize the time series data.

-   line chart represents a series of data points connected by a straight line, with the x-axis representing time and the y-axis representing the data value.

-   We used `geom_line()` object to plot the line chart

-   We used some handy functions from `lubridate` package.. such as `dmy()` function to convert the `character` date type into `date` data type.

-   We also used color aesthetics to differentiate the time series for 3 years.

-   We can convert line chart into area chart using `geom_area()` object

-   We used `geom_point()` aesthetics to change the appearance of points

-   Finally, we used `geom_ribbon()` object to show the confidence region around the line chart..
