---
title: "Making scatter plot in ggplot2"
author: "Siddharth"
date: "`r Sys.Date()`"
output: html_document
---

## Load the Data-set and tidyverse library

```{r}

library(tidyverse)

movies <- read.csv("E:\\Training Modules\\ggplot package\\scatter plots\\IMDB Movies.csv")

#movies <- read.csv("https://raw.githubusercontent.com/siddharth-sahasrabudhe/ggplot2-package---data-visualisation-in-R/main/IMDB%20Movies.csv")



```

## View the data

```{r}

view(movies)

movies %>% colnames()

```

## Generate the scatter plot

```{r}

ggplot(data=movies)+
  aes(x=Duration..min.,y=Gross.Revenue)+
  geom_point()+
  theme_light()
  

```

## Use transparency option to remove overplotting

```{r}
ggplot(data=movies)+
  aes(x=Duration..min.,y=Gross.Revenue)+
  geom_point(alpha=0.2)+
  theme_light()

```

## Use jitter argument to remove overplotting

```{r}

ggplot(data=movies)+
  aes(x=Duration..min.,y=Gross.Revenue)+
  geom_jitter()+
  theme_light()

```

## Add smooth line to check the trend in the data

```{r}
ggplot(data=movies)+
  aes(x=Duration..min.,y=Gross.Revenue)+
  geom_jitter()+
  theme_light()+
  geom_smooth(method="lm",se=FALSE)

```

## Check correlation using Pearson's correlation

```{r}

movies %>%
  {(cor(.$Gross.Revenue,.$Duration..min.,use="complete.obs"))}
```

## Summary:

-   Scatter plot is used to visualize the relationship between two numeric variable

-   `geom jitter()` adds a little random noise to the data which can help avoid overplotting.

-   `geom_smooth()` adds a trend line to scatter plot

-   Using `alpha` parameter we can change the transparency of the points which help avoid overplotting
