---
title: "Stacked bar charts using ggplot function"
author: "Siddharth"
date: "`r Sys.Date()`"
output: html_document
---

### What is stacked bar chart?

Stacked bar charts usually represent a series of bars or columns stacked on top of one another. They are widely used to effectively portray comparisons of total values across several categories.

We will use titanic data-set to carry out EDA using stacked bar chart We will try to find out the answers to following questions:

-   Out of total male and female passengers on the Titanic ship, how many of them are survived?

-   Does survival rate of passengers has any bearing on its socio-economic class?

-   What is survival percentage of male and female passengers?

-   What is survival percentage of passengers based on socio-economic class?

### Load the Data-set:

```{r}

library(tidyverse)

titanic_df <- read.csv("titanic.csv")

# titanic_df <- read.csv("https://raw.githubusercontent.com/siddharth-sahasrabudhe/ggplot2-package---data-visualisation-in-R/main/titanic.csv")

head(titanic_df)

```

### Prepare data transformation:

```{r}

titanic_df1 <- titanic_df %>%
  select(Survived,Pclass,Sex)%>%
  mutate(Survived = factor(Survived,
                           levels=c(0,1),
                           labels=c("Not survived","survived")))%>%
    mutate(Pclass = factor(Pclass,
                           levels=c(1,2,3),
                           labels=c("First class","second class","third class")))%>%
  mutate(Sex=factor(Sex))%>%
  view
  

```

### Generate the Factor summary:

```{r}

titanic_df1 %>%
  map(fct_count)

```

### Prepare contingency table:

```{r}

con_gender <- data.frame(table(titanic_df1$Sex,titanic_df1$Survived))%>%
  view

con_pclass <- data.frame(table(titanic_df1$Pclass,titanic_df1$Survived))%>%
  view

```

## Question #1:

### Out of total male and female passengers on the Titanic ship, how many of them are survived?

```{r}

ggplot(data=con_gender)+
  aes(x=Var1,y=Freq,fill=Var2)+
  geom_col(color="black",position = "stack")+
  geom_text(aes(label=Freq),size=5,position = position_stack(vjust=0.5))+
  scale_fill_brewer(palette = "Pastel1")

  

```

## Question #2:

### What is survival rate of passengers as per their socio-economic status?

```{r}

ggplot(data=con_pclass)+
  aes(x=Var1,y=Freq,fill=Var2)+
  geom_col(color="black",position = "stack")+
  geom_text(aes(label=Freq),size=5,position = position_stack(vjust=0.5))+
  scale_fill_brewer(palette = "Pastel1")

```

## Question #3:

### What is survival percentage of different passenger classes?

```{r}

ggplot(data=con_pclass)+
  aes(x=Var1,y=Freq,fill=Var2)+
  geom_col(color="black",position = "fill")+
  scale_y_continuous(labels = scales::percent)+
  scale_fill_brewer(palette = "Pastel1")

```

## Question #4:

### What is survival percentage of Male and Female passengers?

```{r}

ggplot(data=con_gender)+
  aes(x=Var1,y=Freq,fill=Var2)+
  geom_col(color="black",position = "fill")+
  scale_y_continuous(labels = scales::percent)+
  scale_fill_brewer(palette = "Pastel1")
```

### Summary:

-   Stacked bar charts usually represent a series of bars or columns stacked on top of one another. They are widely used to effectively portray comparisons of total values across several categories.

-   Use statistical transformation - position = "stack" for creating stacked bar chart.

-   Proportionate stacked bar chart shows relative proportions for each category standardized to 100% scale.

-   Use statistical transformation - position = "fill" for creating proportionate stacked bar chart.

-   contingency table is in matrix format that generates multivariate frequency distribution of the variables.
